### 2016-03-09 paper/algorithm.tex
yasu

\section{Swarm Fusion Method}
\yasu{need to polish, reads very bad.}  {\it Swarm Fusion} (SF) is a
natural parallel extension of Fusion Move method (FM). Take a
multi-threading environment to explain our idea, but the technique is also
applicable to other parallel programming model such as {\it MapReduce}
in cloud computing.
%
Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion, while FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. We have 1) a {\it proposal pool}, from which we pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we pick arbitrary number of
intermediate solutions generated by all the threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

Two parameters $\alpha_i$ and $\beta_i$
control the behavior of each fusion step in $T_i$. The thread collects
$\alpha_i$ solution proposals from the proposal pool and $\beta_i$
solutions from the solution pool for fusion in each step.
%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

@@

\mysubsubsection{Base architecture}
The swarm fusion is highly flexible, and we first introduce our base
architecture that exploits general strenghts offered by the
framework. Later, we explain how to further optimize the configuration
to boost performance for specific problems. In the base architecture,
all the threads fuse some number of proposals from the proposal pool and
some number of solutions from the solution pool in each step. In other
words, all the threads constantly exchange solutions while injecting new
proposals. This architecture is illustrated in Figure~\ref{fig:base}.

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf}
 \caption{Base Swarm Fusion architecture.}\label{fig:base}
\end{figure}

>>>>

\section{Swarm Fusion Method}
{\it Swarm Fusion} (SF) is a natural extension of Fusion Move method
(FM). Take a multi-threading environment to explain our idea, but the
technique is also applicable to other parallel programming model such as
{\it MapReduce} in cloud computing.
%
Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
expansion picks one label in each iteration to perform fusion. FM
invokes one proposal generation scheme and generate a solution proposal
for fusion. We have 1) a {\it proposal pool}, from which we can pick
arbitrary number of proposal generation schemes and generate proposals,
and 2) a {\it solution pool}, from which we can pick arbitrary number of
intermediate solutions generated by all the other threads.
%
% Traditional FM has a set of proposal generation schemes to be
% invoked
%
% There are two places to
% collect solutions or solution proposals for fusion. First, the {\it
% proposal pool} can generate new solution proposals on request.
% %
% Second, the {\it solution pool} stores the solutions that have been
% fused by the threads.
In our base configuration, the solution pool only remembers one (the
best) solution generated by each thread, but the scheme can be more
general.

SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
$T_i$), determining the processing flow of the algorithm: In each fusion
step, the thread collects $\alpha_i$ solution proposals from the
proposal pool and $\beta_i$ solutions from the solution pool.
The bottom right configuration in Figure~\ref{fig:model}

\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/model.pdf}
 \caption{Base Swarm Fusion architecture.}\label{fig:model}
\end{figure}

%
Furthermore, one can also control how to choose proposal generation
schemes and/or solutions from the pools.

@@

\mysubsubsection{Base architecture}
The swarm fusion is highly flexible, and we first introduce our base
architecture that exploits general strenghts offered by the
framework. Later, we explain how to further optimize the configuration
to boost performance for specific problems. In the base architecture,
all the threads fuse some number of proposals from the proposal pool and
some number of solutions from the solution pool in each step. In other
words, all the threads constantly exchange solutions while injecting new
proposals. This architecture is illustrated in Figure~\ref{fig:model}.
